Draft_spatio

### 2021-07-27 R/DESIGNATION_DRAFT.Rmd
Corrections (cleaninventory)

inventory = addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))) #3539 rows (Paracou: 3620 rows)
speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "0"
objective = 20
diversification = TRUE
specieslax = FALSE
objectivelax = FALSE
advancedloggingparameters = loggingparameters()
# MainTrail

>>>>

inventory = addtreedim(inventorycheckformat(Paracou6_2016))) #3539 rows (Paracou: 3620 rows)
speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "0"
objective = 20
diversification = TRUE
specieslax = FALSE
objectivelax = FALSE
advancedloggingparameters = loggingparameters()
# MainTrail

### 2021-07-27 R/Draft_spatio.Rmd
Corrections (cleaninventory)

---
title: "Draft_spatio"
author: "Vincyane Badouard"
date: "13/07/2021"
output: html_document
---
```{r}
inventory = ONFGuyafortaxojoin(addtreedim(cleaninventory(inventorycheckformat(Paracou6_2016))))

>>>>

---
title: "Draft_spatio"
author: "Vincyane Badouard"
date: "13/07/2021"
output: html_document
---
```{r}
inventory = ONFGuyafortaxojoin(addtreedim(inventorycheckformat(Paracou6_2016))))
